MYC overrides HIF-1α to regulate proliferating primary cell metabolism in hypoxia

### 2023-04-27 manuscript/manuscript.qmd
add nadp figures

>>>>

In addition to these differential effects on polar metabolite levels, we reasoned that another critical difference between hypoxia and BAY treatment is the impact of hypoxia on cellular redox state. We measured the impact of these treatments on intracellular NAD(H) and NADP(H) redox couples (**Figure 9 - figure supplement 2**). As expected, hypoxia increased the NADH/NAD^+^ ratio, driven primarily by a decrease in intracellular NAD^+^. Interestingly, while BAY treatment increased the levels of NADH, a concomitant increase in NAD^+^ resulted in preservation of the NADH/NAD^+^ ratio. As NADH accumulation is a putative inhibitor of glycolytic flux [@tilton1991], this may be one mechanism by which glycolytic flux is decreased in hypoxia but not following BAY treatment. Conversely, hypoxia decreased the NADPH/NADP^+^ ratio in both control and BAY treated cells, primarily through decreasing NADPH. This finding is consistent with prior studies of bovine coronary artery smooth muscle cells [@gupte2006]. In hypoxia, NADPH is primarily generated by the pentose phosphate pathway [@liu2016], where it plays an important role in the detoxification of reactive oxygen species [@fessel2018; @xiao2018]. Although we modeled increased flux through the pentose phosphate pathway in hypoxia (**Figure 5A**), the overall flux was low and apparently inadequate to maintain the NADPH/NADP^+^ ratio.
